Towards Automated Merging of Code Clones in Object-Oriented Programming Languages\\- Work in Progress -

### 2019-05-06 sattose/paper.tex
Updates from Overleaf

\subsection{CloneRefactor}
\todo{this is not background, this is already your research. Background is what others did and you use as foundation}
A 2016 survey by Gautam \cite{gautam2016various} focuses more on various techniques for clone detection. For our tool, we decided to combine AST- and Graph-based approaches for clone detection, similar to Scorpio (which is a clone detection tool that's part of TinyPDG: a library for building intraprocedural program dependency graphs for Java programs). We decided to base our tool on the JavaParser library \cite{tomassetti2017javaparser}, as it supports rewriting the AST back to Java code and is useable with all modern Java versions (Java 1-12). We collect each statement and declaration and compare those to find duplicates. This way we build a graph of each statement/declaration linking to each subsequent statement/declaration (horizontally) and linking to each of its duplicates (vertically). This is displayed in figure \ref{fig:clonerefactor}.

@@

\subsection{Thresholds}
CloneRefactor works on basis of three thresholds for finding clones:
\begin{enumerate}
  \item \textbf{Number of statements/declarations:} The number of statements/declarations that should be equal/similar for it to be considered a clone.
  \item \textbf{Number of tokens:} The number of tokens (excluding whitespace, end-of-line terminators and comments) that should be equal/similar for it to be considered a clone.
  \item \textbf{Number of lines:} The minimum amount of lines (excluding lines that do not contain any tokens, for tokens same exclusions apply) that should be equal/similar for it to be considered a clone.
\end{enumerate}
Of course, if any threshold is set to zero, it will be ignored, thus not all thresholds have to be used at all times. We consider ``number of lines'' to be the least important, as it highly depends on the programmer of the codebase (and we do not want this kind of dependence!). On basis of manual assessment, we have determined that setting the ``number of statements/declarations'' to 6 ensures that most non-harmful clones are filtered out. On the downside, this also filters out some harmful antipatterns, for instance, if a cloned line has many tokens we might want to consider a clone if it spans less than 6 statements (as a cloned line with many tokens is more harmful than one with few).

@@

\subsection{The corpus}
For our measurements we use a large corpus of open source projects \cite{githubCorpus2013}\footnote{The corpus can be downloaded from the following URL: \url{http://groups.inf.ed.ac.uk/cup/javaGithub/java_projects.tar.gz}}. This corpus has been assembled to contain relatively higher quality projects (by filtering by forks). Also, any duplicate projects were removed from this corpus. This results in a variety of Java projects that reflect the quality of average open source Java systems and are useful to perform measurements on.

@@

\subsubsection{Our measurements}
We use a similar setup to that used in the study of \todo{put here the concise description of the experiment}  (Table~3 in Fontana et al) \cite{fontana2015duplicated}, but with the following differences in our setup:
\begin{itemize}
  \item We consider clone classes rather than clone pairs.
\item We use different thresholds regarding when a clone should be considered.
\item We seek by statement/declaration rather than SLOC.
\item We test a broader range of projects (they use a set of 50 relatively large projects, we use a large corpus that was assembled by a machine learning algorithm testing java projects on GitHub for quality, which contains projects of all sizes and with differing code quality).
\end{itemize}

>>>>

\subsection{CloneRefactor}
A 2016 survey by Gautam \cite{gautam2016various} focuses more on various techniques for clone detection. For our tool, we decided to combine AST- and Graph-based approaches for clone detection, similar to Scorpio \footnote{Scorpio is a clone detection tool that's part of TinyPDG: a library for building intraprocedural program dependency graphs for Java programs.}. We decided to base our tool on the JavaParser library \cite{tomassetti2017javaparser}, as it supports rewriting the AST back to Java code and is useable with all modern Java versions (Java 1-12). We collect each statement and declaration and compare those to find duplicates. This way we build a graph of each statement/declaration linking to each subsequent statement/declaration (horizontally) and linking to each of its duplicates (vertically). This is displayed in figure \ref{fig:clonerefactor}.

@@

\subsubsection{Detection of clone classes}\label{chap:cloneclasses}
For CloneRefactor, we have chosen to focus on the detection of clone classes rather than clone pairs. We did this because clone pairs don’t provide a general overview of all entities containing the clones, with all their related issues and characteristics \cite{fontana2012duplicated}. On the other hand, clone classes are harder to manage, but they provide all information needed to plan a suitable refactoring strategy, since this way all instances of a clone are considered. Another issue involves clone grouping by pairs: single clone reference amount increases according to binomial coefficient formula (two clones form a pair, three clones form three pairs, four clones form six pairs, and so on), of which a heavy information redundancy follows \cite{fontana2012duplicated}.

\subsubsection{Thresholds}\label{chap:thresholds}
CloneRefactor works on basis of three thresholds for finding clones:
\begin{enumerate}
  \item \textbf{Number of statements/declarations:} The number of statements/declarations that should be equal/similar for it to be considered a clone.
  \item \textbf{Number of tokens:} The number of tokens (excluding whitespace, end-of-line terminators and comments) that should be equal/similar for it to be considered a clone.
  \item \textbf{Number of lines:} The minimum amount of lines (excluding lines that do not contain any tokens, for tokens same exclusions apply) that should be equal/similar for it to be considered a clone.
\end{enumerate}
Of course, if any threshold is set to zero, it will be ignored, thus not all thresholds have to be used at all times. We consider ``number of lines'' to be the least important, as it highly depends on the programmer of the codebase (and we do not want this kind of dependence!). On basis of manual assessment, we have determined that setting the ``number of statements/declarations'' to 6 ensures that most non-harmful clones are filtered out. On the downside, this also filters out some harmful antipatterns, for instance, if a cloned line has many tokens we might want to consider a clone if it spans less than 6 statements (as a cloned line with many tokens is more harmful than one with few).

@@

\subsection{The corpus}\label{chap:corpus}
For our measurements we use a large corpus of open source projects \cite{githubCorpus2013}\footnote{The corpus can be downloaded from the following URL: \url{http://groups.inf.ed.ac.uk/cup/javaGithub/java_projects.tar.gz}}. This corpus has been assembled to contain relatively higher quality projects (by filtering by forks). Also, any duplicate projects were removed from this corpus. This results in a variety of Java projects that reflect the quality of average open source Java systems and are useful to perform measurements on.

@@

\subsubsection{Our measurements}
We use a similar setup to that used in the study of Table~3 in Fontana et al \cite{fontana2015duplicated}. Fontana et al measure clones using their own tool called DCRA. This tool detects clone pairs in Java-based source code. It operates on a single threshold: the minimum number of lines that a clone should span. Our measurements were conducted using CloneRefactor, because of which the setup for our measurements differs as follows from Fontana et al:
\begin{itemize}
  \item We consider clone classes rather than clone pairs. The rationale for this is given in section \ref{chap:cloneclasses}.
\item We use different thresholds regarding when a clone should be considered. Fontana et al seek clones that span a minimum of 7 source lines of code (SLOC). We seek clones with a minimum size of 6 statements/declarations. This is further explained in section \ref{chap:thresholds}.
\item We seek by statement/declaration rather than SLOC. This makes our analysis depend less on the coding style (in terms of newline usage) of the author of the software project.
\item We test a broader range of projects. Fontana et al use a set of 50 relatively large projects. We use the corpus as explained in \ref{chap:corpus}, which contains a diverse set of projects (diverse both in volume and code quality).
\end{itemize}
